For submission to the Journal of Integrated Pest Management

### 2021-08-27 ofv_fife_2021.Rmd
added track revisions version
added abbreviation OFV to caption in Fig 1

Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing (HTS). Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank. Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L. muscari* (Alachua, OFV-Orc2) and *A. elatior* (Leon, OFV-Orc1).

@@

### Figure captions
`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp. infected with orchid fleck virus: (a) ringspot symptoms on *Liriope muscari* cv. 'Gigantea' (b-c) Details of ringspot symptoms on *L. muscari* cv. 'Gigantea' (d) rust colored spots on *Ophiopogon intermedius*")`

>>>>

Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing (HTS). Amplicons shared 98\% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank. Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L. muscari* (Alachua, OFV-Orc2) and *A. elatior* (Leon, OFV-Orc1).

@@

### Figure captions
`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp. infected with orchid fleck virus (OFV): (a) ringspot symptoms on *Liriope muscari* cv. 'Gigantea' (b-c) Details of ringspot symptoms on *L. muscari* cv. 'Gigantea' (d) rust colored spots on *Ophiopogon intermedius*")`
